### 2021-03-11 results/draft.tex
added a conceptual diagram

\subsection{A general model to estimate species distribution from eDNA}
To estimate

@@

>>>>

\subsection{A general model to estimate species distribution from eDNA}
To estimate the spatial distribution from eDNA considering with spatial biases due to degradation from environmental factors (e.g., temperature and advection),

@@

\newpage
\begin{figure}[h]
  \centering
  \includegraphics[width = 18cm]{idea.png}
  \caption{Conceptual diagram of this study.}
\end{figure}
